Explaining Noord-Holland house prices

### 2023-04-04 Paper/paper.Rmd
Update

```{r include=FALSE}
library(mapview)
library(tidyverse)
library(tmap)
library(sf)
setwd("./..")
funda_data <- st_read("data/funda_buy_28-03-2023_full_distances.gpkg")
setwd("Paper")
```

@@

```{r test1, echo=FALSE, message=FALSE, warning=FALSE, fig.cap = "Figure number, Plot of NH"}
tm_shape(funda_data) +
  tm_dots()

>>>>

```{r include=FALSE}
library(mapview)
library(tidyverse)
library(tmap)
library(sf)
setwd("./..")
funda_data <- st_read("data/Houseprices/funda_buy_amsterdam_31-03-2023_full_distances.gpkg")
PC4 <- st_transform(st_read("data/Amsterdam/PC4.json"), crs = 28992)
setwd("Paper")
```

@@

```{r test1, echo=FALSE, fig.cap="Figure number", message=FALSE, warning=FALSE}
#plot dependent variable
# make some bbox magic 
bbox_new <- st_bbox(PC4) # current bounding box 
xrange <- bbox_new$xmax - bbox_new$xmin # range of x values 
yrange <- bbox_new$ymax - bbox_new$ymin # range of y values 
# bbox_new[1] <- bbox_new[1] - (0.25 * xrange) # xmin - left 
bbox_new[3] <- bbox_new[3] + (0.35 * xrange) # xmax - right 
# bbox_new[2] <- bbox_new[2] - (0.25 * yrange) # ymin - bottom 
bbox_new[4] <- bbox_new[4] + (0.25 * yrange) # ymax - top 
bbox_new <- bbox_new %>% # take the bounding box ... 
  st_as_sfc() # ... and make it a sf polygon # looks better, does it?

tm_shape(PC4, bbox = bbox_new)+
  tm_polygons(col = "white")+
  tm_shape(funda_data)+
  tm_dots(c("ndvi500"), title = "NDVI (500m range)", size = 0.1) + 
  tm_layout(title = "Amsterdam NDVI values",
            #title.fontfamily = "cambria",
            title.fontface = "bold",
            #legend.text.fontfamily = "cambria",
            #legend.title.fontfamily = "cambria",
            legend.position = c("right", "top"),
            legend.text.size = 0.75,
            legend.title.size = 1)
